---
title: "世界经济"
author: "qiufei"
date: "2016-01-31"
output: 
  html_document: 
    fig_height: 7
    fig_width: 9
    keep_md: yes
    number_sections: yes
    theme: readable
    toc: yes
---



```{r,Message=FALSE,echo=FALSE,include=FALSE}

# load needed packages
library(knitr)
opts_chunk$set(Message=FALSE,echo=FALSE)
library(ggplot2)
library(reshape2)
library(Quandl)
library(quantmod)
options("getSymbols.warning4.0"=FALSE)
library(miscTools)
library(scales)
library(ggrepel)

```



# world gdp #

## world gdp growth rate ##

```{r}

options(digits = 2)
gdp.wb = Quandl("WWDI/WLD_NY_GDP_MKTP_KD_ZG", api_key="9iGeZZoG6Vc46rfs1AgJ")

gdp.wb.pic = ggplot(data = gdp.wb,aes(x = Date,y = Value))+
      geom_line(colour = 'red')+
      geom_point()+
      geom_text(mapping = aes(label = round(Value,2)))+
    ## 这是给数据点增加数据值标签
      xlab('year')+
      ylab('%')+
      ggtitle('World GDP Growth Rate')

      
gdp.wb.pic  

gdp.wb.median = median(gdp.wb[,2])
gdp.wb.mean = mean(gdp.wb[,2])

gdp.wb.data = kable(gdp.wb,caption = 'World GDP Growth Rate')


```

`r head(gdp.wb[,1],1)`年世界GDP增长率为`r head(gdp.wb[,2],1)`

`r tail(gdp.wb[,1],1)`年以来,世界GDP增速的中位数为`r gdp.wb.median`,均值为`r gdp.wb.mean`

## china gdp growth rate ##


```{r}

cn.gdp.g = Quandl("NBSC/A020A01_A", api_key="9iGeZZoG6Vc46rfs1AgJ")

gdp.cn.pic = ggplot(data = cn.gdp.g,aes(x = Date,y = Value))+
      geom_line(colour = 'red')+
      geom_point()+
      xlab('year')+
      ylab('%')+
      ggtitle('china GDP Growth Rate')

      
gdp.cn.pic 

gdp.cn.median = median(cn.gdp.g[,2])
gdp.cn.mean = mean(cn.gdp.g[,2])

gdp.cn.g.data = kable(cn.gdp.g,caption = 'china GDP Growth Rate')


```

`r head(cn.gdp.g[,1],1)`年中国GDP增长率为`r head(cn.gdp.g[,2],1)`

`r tail(cn.gdp.g[,1],1)`年以来,中国GDP增速的中位数为`r gdp.cn.median`,均值为`r gdp.cn.mean`


##  world gdp per capita growth rate ##

```{r}

gdp.p.g.wb = Quandl("WWDI/WLD_NY_GDP_PCAP_KD_ZG", api_key="9iGeZZoG6Vc46rfs1AgJ")

gdp.p.g.pic = ggplot(data = gdp.p.g.wb,aes(x = Date,y = Value,labels = Value))+
      geom_line(colour = 'red')+
      geom_point()+
      xlab('year')+
      ylab('%')+
      ggtitle('World GDP per capita Growth Rate')
      
gdp.p.g.pic  

gdp.p.median = median(gdp.p.g.wb[,2])
gdp.p.mean = mean(gdp.p.g.wb[,2])

gdp.p.g.data = kable(gdp.p.g.wb,caption = 'World GDP per capita Growth Rate')

```

`r head(gdp.p.g.wb[,1],1)`年世界人均GDP增长率为`r head(gdp.p.g.wb[,2],1)`


世界人均GDP增速的中位数为`r gdp.p.median`,均值为`r gdp.p.mean`



## world gdp per capita current price ##

```{r}

gdp.p.wb = Quandl("WWDI/WLD_NY_GDP_PCAP_CD", api_key="9iGeZZoG6Vc46rfs1AgJ")
## 
gdp.p.wb.pic = ggplot(data = gdp.p.wb,aes(x = Date,y = Value))+geom_line(colour = 'red')+geom_point()+ggtitle('World GDP per capital, cunrrent US dollar')+xlab('year')+ylab('$')
## 
gdp.p.wb.pic

gdp.p.wb.1978 = gdp.p.wb[grep('1978',gdp.p.wb$Date),]
gdp.p.wb.recent = head(gdp.p.wb,1)
gdp.p.wb.growth = gdp.p.wb.recent[,2]/gdp.p.wb.1978[,2]

```

`r head(gdp.p.wb[,1],1)`年世界人均GDP为`r head(gdp.p.wb[,2],1)`美元(现价).

不考虑通胀因素,世界人均GDP`r gdp.p.wb.recent[,1]`是`r gdp.p.wb.1978[,1]`的`r gdp.p.wb.growth`倍.


## china gdp per capita current price ##


```{r}

gdp.p.cn = Quandl("NBSC/A020106_A", api_key="9iGeZZoG6Vc46rfs1AgJ")

gdp.p.cn.pic = ggplot(data = gdp.p.cn,aes(x = Date,y = Value))+geom_line(colour = 'red')+geom_point()+ggtitle('China GDP per capital, cunrrent Yuan')+xlab('year')+ylab('Yuan')


gdp.p.cn.1978 = gdp.p.cn[grep('1978',gdp.p.cn$Date),]
gdp.p.cn.recent = head(gdp.p.cn,1)
gdp.p.cn.growth = gdp.p.cn.recent[,2]/gdp.p.cn.1978[,2]

```

`r head(gdp.p.cn[,1],1)`年中国人均GDP为`r head(gdp.p.cn[,2],1)`元(现价).

不考虑通胀因素,中国人均GDP`r gdp.p.cn.recent[,1]`是`r gdp.p.cn.1978[,1]`的`r gdp.p.cn.growth`倍.


## world GDP per capita constant price ##


```{r}

gdp.p.constant.fed = Quandl("FRED/NYGDPPCAPKDWLD", api_key="9iGeZZoG6Vc46rfs1AgJ")
## 
gdp.p.constant.fed.pic = ggplot(data = gdp.p.constant.fed,aes(x = DATE,y = VALUE))+geom_line(colour = 'red')+geom_point()+ggtitle('World GDP per capital, constant US dollar')+xlab('year')+ylab('$')
## 
gdp.p.constant.fed.pic
## 
gdp.p.constant.1978 = gdp.p.constant.fed[grep('1978',gdp.p.constant.fed$DATE),]
gdp.p.constant.recent = head(gdp.p.constant.fed,1)
gdp.p.constant.growth = gdp.p.constant.recent[,2]/gdp.p.constant.1978[,2]


```
`r head(gdp.p.constant.fed[,1],1)`年世界不变价人均GDP为`r head(gdp.p.constant.fed[,2],1)`美元(1960年不变价).



不变价世界人均GDP`r gdp.p.constant.recent[,1]`是`r gdp.p.constant.1978[,1]`的`r gdp.p.constant.growth`倍.

基本上人均GDP的绝对值出现下降的年份都是危机的年份.


## china GDP per capita constant price ##

```{r}

gdp.p.constant.cn = Quandl("FRED/NYGDPPCAPKDCHN", api_key="9iGeZZoG6Vc46rfs1AgJ")  
## 
gdp.p.constant.cn.pic = ggplot(data = gdp.p.cn,aes(x = DATE,y = VALUE))+geom_line(colour = 'red')+geom_point()+ggtitle('China GDP per capital, cunrrent Yuan')+xlab('year')+ylab('Yuan')
## 
gdp.p.constant.cn.1978 = gdp.p.constant.cn[grep('1978',gdp.p.constant.cn$DATE),]
gdp.p.constant.cn.recent = head(gdp.p.constant.cn,1)
gdp.p.constant.cn.growth = gdp.p.constant.cn.recent[,2]/gdp.p.constant.cn.1978[,2]


```

`r head(gdp.p.constant.cn[,1],1)`年中国不变价人均GDP为`r head(gdp.p.constant.cn[,2],1)`元.

中国不变价人均GDP`r gdp.p.constant.cn.recent[,1]`是`r gdp.p.constant.cn.1978[,1]`的`r gdp.p.constant.cn.growth`倍.




# trade #

```{r}

trade.in.gdp = Quandl("WWDI/WLD_NE_TRD_GNFS_ZS", api_key="9iGeZZoG6Vc46rfs1AgJ")

trade.in.gdp.pic = ggplot(data = trade.in.gdp,aes(x = Date,y = Value,labels = Value))+
      geom_line(colour = 'red')+
      geom_point()+
      xlab('year')+
      ylab('%')+
      ggtitle('World trade share of GDP')
      
trade.in.gdp.pic

trade.in.gdp.median = median(trade.in.gdp[,2])
trade.in.gdp.mean = mean(trade.in.gdp[,2])

trade.in.gdp.data = kable(trade.in.gdp,caption = 'World trade share of GDP')

```
`r head(trade.in.gdp[,1],1)`世界贸易占GDP的比重为`r head(trade.in.gdp[,2],1)`

世界贸易占GDP比重的中位数为`r trade.in.gdp.median`,均值为`r trade.in.gdp.mean`
