---
title: "中央银行报告"
author: "qiufei"
date: "2016-05-19"
output: 
  html_document: 
    fig_height: 7
    fig_width: 9
    keep_md: yes
    number_sections: yes
    theme: readable
    toc: yes
---

```{r setup,Message=FALSE,echo=FALSE,include=FALSE,warning=FALSE}

# load needed packages
library(knitr)
opts_chunk$set(Message=FALSE,echo=FALSE)
library(ggplot2)
library(reshape2)
library(Quandl)
library(quantmod)
options("getSymbols.warning4.0"=FALSE)
library(scales)
library(plyr)
library(dplyr)
## options(warn=-1)                        #suprress warning globally
## the default is
## options(warn=0)
## get data from fed
fedata = function(x.name){
    getSymbols(x.name,
               src = "FRED",
               auto.assign=FALSE #让getsymbol不要自动取名字
                         )}
## get data from quandl.com
qdata = function(x.name){
    Quandl(x.name, api_key="9iGeZZoG6Vc46rfs1AgJ")}
## pic
## define needed functions
## 
simpic.f = function(code,label){
    raw = getSymbols.FRED(code,auto.assign=FALSE)
    raw.median = median(coredata(raw),na.rm = TRUE)
    detail = summary(raw)[,2]
    print(detail)
    chartSeries(raw,name = label)
}
## 
simpic.q = function(code,label){
    raw = Quandl(code, api_key="9iGeZZoG6Vc46rfs1AgJ")
    raw = as.xts(raw[,-1],order.by = raw[,1])
    detail = summary(raw)[,2]
    print(detail)
    chartSeries(raw,name = label)
}
##
twopic = function(data,colname2,colname3,label){
    colnames(data) = c('year',colname2,colname3)
    pic.data = melt(data,id = 'year')
    ggplot(pic.data,aes(x = year,y = value,color = variable))+
        geom_line()+
        geom_point(size=0.5)+
        ggtitle(label)
}


```

this is report of major central banks.

# The labor market

Labor market conditions strengthened further across a variety of dimensions over the second half of 2015.

## employment numbers ##


```{r labor market}

## Thousands of Persons Seasonally Adjusted, All Employees: Total nonfarm.
usa.employ = qdata("FRED/PAYEMS")
ggplot(usa.employ,aes(x = DATE,y = VALUE))+
    geom_line(color = 'red')

## get monthly added employ numbers
usa.employ = arrange(usa.employ,DATE)
usa.employ$add.employ =c(NA,diff(usa.employ$VALUE))


ggplot(usa.employ,aes(x = DATE,y = add.employ))+
    geom_line(color = 'red')+
    ggtitle('monthly added employment since 1939 of USA')


ggplot(filter(usa.employ,DATE>='2009-01-01'),aes(x = DATE,y = add.employ))+
    geom_line(color = 'red')+
    geom_point()+
    ggtitle('monthly added employment since 2009 of USA')

```

## employment rate ##

Changing demographics--most notably the increasing share of older people in the population, who are less likely to be in the labor force--and other longer-run structural changes in the labor market have continued to push down the participation rate even as cyclical forces have been pushing it up.

That said, labor force participation appears to remain a little weaker than can be explained by structural factors alone, pointing to the likelihood that some slack remains in this dimension of labor utilization.

In addition, although the share of workers who are employed part time but would like to work full time has fallen noticeably since June, it is still relatively high, indicating some scope for improvement on this dimension as well.

```{r }

## Unemployment Rate: Aged 15-64: All Persons for the United States
usa.unemploy = fedata('LRUN64TTUSQ156S')
chartSeries(usa.unemploy)
##  unemployment rate--which had reached 10 percent in late 2009

## usa labor force participant rate
usa.participant = fedata('CIVPART')
chartSeries(usa.participant)

## Labor Force Participation Rate = Labor Force / Civilian Non-Institutionalized Population 

## where the Labor Force = Employed + Unemployed

## Civilian Non-institutional Population - Everyone living in the U.S. who is 16 or older MINUS inmates of institutions such as prisons, nursing homes and mental hospitals and MINUS those on active duty in the Armed Forces.

## People who would like work, but haven't ACTIVELY looked for it in the last month are NOT counted as being in the labor force no matter how much they want a job. 

##
## Employment-Population Ratio
##
usa.ep.ratio = fedata('LNU02300000')
chartSeries(usa.ep.ratio,name = 'Employment-Population Ratio of USA')

summary(usa.ep.ratio)

##
## compare paticipant rate and emloyment rate
## 
usa.labor = cbind(usa.participant,usa.ep.ratio)
colnames(usa.labor) = c('participant','employ')
## 
usa.labor.str = data.frame(
    date = time(usa.labor),
    coredata(usa.labor))
## 
usa.labor.str.long = melt(usa.labor.str,id = 'date')
## 
ggplot(usa.labor.str.long,aes(x = date,y = value,group = variable,color = variable))+geom_line()  

```



## labor compensation ##

compensation per hour in the business sector--a volatile measure derived from the labor compensation data in the national income and product accounts, or NIPA--is reported to have increased more quickly in 2015 than its average pace throughout most of the recovery.

the employment cost index for private industry workers, which measures both wages and the cost to employers of providing benefits, increased about 2 percent over the 12 months ending in December, similar to the pace seen throughout most of the recovery. All of these measures of compensation are increasing at slower rates than those seen prior to the recession.

This deceleration probably reflects a variety of factors, including the slower growth of productivity, the slower pace of inflation, and perhaps some remaining slack in the labor market. 

```{r }

##
##  Real Compensation Per Hour
##
usa.wage.manufac = fedata('COMPRMS') %>% chartSeries(name = 'Manufacturing Sector Real Compensation Per Hour of USA')

usa.wage.business = fedata('RCPHBS') %>% chartSeries(name = 'Business Sector Real Compensation Per Hour of USA')

usa.employ.cost = fedata('ECICOM') %>% chartSeries(name = ' employment cost index for private industry workers of USA')
 

```

## labor productivity ##

```{r }

usa.productivity = fedata('OPHPBS')
chartSeries(usa.productivity)
usa.productivity = data.frame(
    date = time(usa.productivity),
    coredata(usa.productivity))
colnames(usa.productivity) = c('date','value')

usa.productivity = arrange(usa.productivity,date)
usa.productivity$change = c(NA,diff(usa.productivity$value))

ggplot(usa.productivity,aes(x = date,y = change))+
    geom_line(color='red')+
    geom_point()+
    ggtitle('change of Business Sector  Real Output Per Hour/USA')

tail(usa.productivity,16)

summary(usa.productivity$change)

```

从这里来看,美国的劳动生产率并没有下降很多啊?为什么美国人都在讨论劳动生产率下降的问题?

# prices #


## oil prices ##

Futures prices have also dropped significantly and indicate that market participants expect only modest price increases over the next few years. 

```{r oil price}

##
## Crude Oil Prices: Brent - Europe
##
oil.brent = fedata('DCOILBRENTEU')
chartSeries(oil.brent,name = 'Crude Oil Spot Prices: Brent - Europe')


oil.brent.future = qdata('CME/BZZ2017')

ggplot(filter(oil.brent.future,Date>='2015-01-01'),aes(x = Date,y = Settle))+
    geom_line(color='red')+
    ggtitle('Brent Crude Oil Financial Futures, December 2017 (BZZ2017)')

## latest future price
head(oil.brent.future$Settle,1)
## latest spot price
tail(oil.brent,1)


ggplot(filter(oil.brent.future,Date>='2015-01-01'),
       aes(x = Date,y = Change))+
    geom_line(color='red')+
    ggtitle('price change of Brent Crude Oil Financial Futures, December 2017 (BZZ2017)')


```

## cpi ##

```{r cpi}

pce = fedata('PCE')

chartSeries(pce)
chartSeries(pce['2007-01-01/',])

```

## exchange rate ##

The broad dollar has appreciated more than 20 percent since the middle of 2014, reflecting both heightened concerns about the global outlook, which have resulted in safe-haven flows toward dollar asset

```{r exchange rate}

usa.exchange = fedata('TWEXBPA')
chartSeries(usa.exchange)

```

# GDP #

## Quarterly Percent Change from Preceding Period  ##

Quarterly, Seasonally Adjusted Annual Rate

```{r }

gdp.g.chain = fedata('A191RL1Q225SBEA')
chartSeries(gdp.g.chain,name = 'USA GDP Quarterly Percent Change from Preceding Period')

```

## Quarterly Percent Change from Quarter One Year Ago  ##

Quarterly, Seasonally Adjusted

```{r }

gdp.g.previous = fedata('A191RO1Q156NBEA')
chartSeries(gdp.g.previous,name = 'USA GDP Quarterly Percent Change from Quarter One Year Ago')

tail(gdp.g.previous)

```

## annually Percent Change from Preceding Period  ##

Annual, Not Seasonally Adjusted

```{r annul gdp growth rate}

gdp.g.annual = fedata('A191RL1A225NBEA')
chartSeries(gdp.g.annual)

tail(gdp.g.annual)

```

http://www.federalreserve.gov/monetarypolicy/mpr_20160210_part1.htm


# house #

## 房价 ##

```{r house price}

house.price = fedata('SPCS20RSA')
  chartSeries(house.price)

```

# 债务占可支配收入的比重 #

也就是说在顶峰时期,美国家庭债务支出占可支配收入的比重不超过20%?

```{r house debt ratio}

debt.ratio = qdata('FRED/TDSP')
ggplot(debt.ratio,aes(x = DATE,y = VALUE))+
    geom_line(color = 'red')+
    ggtitle('Household Debt Service Payments as a Percent of Disposable Personal Income of USA')


obligation.ratio = qdata('FRED/FODSP')

ggplot(obligation.ratio,aes(x = DATE,y = VALUE))+
    geom_line(color = 'red')+
    ggtitle('美国家庭金融债务支出占可支配收入的比重')


```

# investment #

## Real Private Nonresidential Fixed Investment ##

Billions of Chained 2009 Dollars

```{r invest}

invest = fedata('PNFIC1')
chartSeries(invest)
  

```



# fiscal policy #

## Percent Change from Preceding Period ##

Quarterly, Seasonally Adjusted Annual Rate.

```{r }

simpic.f('A822RL1Q225SBEA','chain change of Real Government Consumption Expenditures and Gross Investment ')  

```

## Percent Change from Quarter One Year Ago  ##
Percent Change from Quarter One Year Ago.
Quarterly, Seasonally Adjusted.

```{r }

simpic.f('A822RO1Q156NBEA','change of Real Government Consumption Expenditures and Gross Investment ')  

```

## surplus ##

```{r surplus}

receipt = qdata('OMB/14_1')
expenditure = qdata('OMB/14_3')
p.receipt = filter(receipt,receipt[,1]>='1950-12-31')
p.expenditure = filter(expenditure,expenditure[,1]>='1950-12-31')
fiscal.pic = cbind.data.frame(p.receipt[,c(1,9)],p.expenditure[,c(1,3)])
fiscal.pic = fiscal.pic[,-3]
twopic(fiscal.pic,'receipt','expenditure','deficit and surplus of USA % of GDP')

```

# trade #

## growth rate ##

```{r }

export.rate = qdata('FRED/A020RO1Q156NBEA')
import.rate = qdata('FRED/A021RO1Q156NBEA')
trade.rate = cbind(export.rate,import.rate)
trade.rate = trade.rate[,-3]
twopic(trade.rate,'export','import','export and import grwoth rate of USA')


```

## current account percent ##

```{r }

simpic.q('ODA/USA_BCA_NGDPD','United States Current Account Balance, % of GDP')

```


# financial developments #


## Effective Federal Funds Rate ##

```{r}

simpic.f('FEDFUNDS','Effective Federal Funds Rate')  

```

## bond ##

### USA Treasury Inflation-Indexed Security ##

Long-Term Government Bond Yields

```{r tips}

simpic.f('FII10','10-Year Treasury Inflation-Indexed Security, Constant Maturity')

simpic.f('TP30A28','30-Year Treasury Inflation-Indexed Bond')  

```

### 'Moody Seasoned Aaa Corporate Bond Yield ##
```{r}

simpic.f('AAA','Moody Seasoned Aaa Corporate Bond Yield')  

```

### Moody's Seasoned Aaa Corporate Bond Yield Relative to Yield on 10-Year Treasury Constant Maturity ##

```{r}

simpic.f('AAA10YM','Moody Seasoned Aaa  Relative to 10-Year Treasury Constant Maturity')  

```



## risk spread ##

### St. Louis Fed Financial Stress Index ##

```{r}

simpic.f('STLFSI','St. Louis Fed Financial Stress Index')  

```


### CBOE volatility index ##

in the short run, there is a strong negative correlation between volatility index and the level of the market.

```{r volatility}

simpic.f('VIXCLS','CBOE Volatility Index')

simpic.f('VXOCLS','CBOE S&P 100 Volatility Index')

```


### BofA Merrill Lynch US Corporate AAA Option-Adjusted Spread ##

```{r}

simpic.f('BAMLC0A1CAAA','AAA Option-Adjusted Spread')  

```

### BofA Merrill Lynch US High Yield CCC or Below Option-Adjusted Spread ##

```{r}

simpic.f('BAMLH0A3HYC','CCC or Below Option-Adjusted Spread')  

```

## stock market ##

1. historically stocks have returned between 6 and 7 percent after inflation over the last two centuries and have sold at an average PE ratio of about 15.

### country stock market comparison ###

```{r stock compare}

qfdata = function(x){
    dat = qdata(x)
    xts(dat[,-1],order.by = dat[,1])}

## japan.stock = qfdata('TSE/TOPIX')
## japan.stock = japan.stock[,'Close']
japan.stock = fedata('NIKKEI225')
euro.stock = qfdata('GOOG/NYSE_FEU')
euro.stock = euro.stock[,'Close']
china.stock = qfdata('YAHOO/SS_000001')
china.stock = china.stock[,'Close']
## new.market = qfdata('NASDAQOMX/NQEM')
## new.market = new.market[,1]
## 新兴市场指数与中国股市相关性很高
usa.stock = qfdata('YAHOO/INDEX_GSPC')
usa.stock = usa.stock[,'Close']

stock.major = cbind(japan.stock,euro.stock,china.stock,usa.stock)
stock.major = data.frame(time(stock.major),coredata(stock.major))
colnames(stock.major) = c('date','japan','euro','china','usa')
stock.major[,2:5] = scale(stock.major[,2:5])
stock.major = filter(stock.major,date>='1985-07-03')
stock.major.pic = melt(stock.major,id = 'date')

ggplot(stock.major.pic,aes(x = date,y = value,color = variable))+
    geom_line()+
    ggtitle('主要经济体股指表现(数据经标准化)')

```



### s&p ##

of the top 20 firms,15 belongs to two industries: consumer staples and healthcare.

```{r sp500}

simpic.f('SP500','S&P 500')  

```


### Dow Jones Industrial Average ##

```{r dj}

simpic.f('DJIA','Dow Jones Industrial Average')

```

### sp and dow in one pic ###

```{r stock}

sp = fedata('SP500')
dow = fedata('DJIA')
sp.dow = cbind(sp,dow)
sp.dow = data.frame(year = time(sp.dow),coredata(sp.dow))
sp.dow[,2:3] = scale(sp.dow[,2:3])
twopic(sp.dow,'sp500','djia','sp500 and Dow Jones Industrial Average')
  

```


## credit ##

```{r credit}

bank.credit = fedata('DDDI01USA156NWDB')
all.credit = fedata('DDDI12USA156NWDB')
credit = cbind(bank.credit,all.credit)
credit = data.frame(year = time(credit),coredata(credit))
twopic(credit,'银行贷款/GDP','所有金融机构贷款/GDP','美国贷款占GDP比重')

```

### credit world comparison ###

Private Credit by Deposit Money Banks and Other Financial Institutions to GDP.


```{r all credit}

usa.credit = fedata('DDDI12USA156NWDB')
china.credit = fedata('DDDI12CNA156NWDB')
german.credit = fedata('DDDI12DEA156NWDB')
japan.credit = fedata('DDDI12JPA156NWDB')
world.credit = fedata('DDDI121WA156NWDB')

credit.all = cbind(usa.credit,china.credit,german.credit,japan.credit,world.credit)
credit.all = data.frame(year = time(credit.all),coredata(credit.all))
colnames(credit.all) = c('year','美国','中国','德国','日本','世界')

credit.pic = melt(credit.all,id = 'year',variable = '国家')

ggplot(credit.pic,aes(x = year,y = value,color = 国家,shape = 国家))+
    geom_line()+
    geom_point()+
    annotate('rect',xmin = as.Date('2007-01-01'),xmax = as.Date('2008-01-01'),ymin = 0,ymax = 200,alpha=0.1,fill = 'green')+
    ggtitle('信贷与GDP比重(%)') 

```

浅绿色柱状带标出的是2007,2008两年间的数据.

1. 中国信贷占GDP的比重不是最高的.
最上面蓝色与红色分别是日本和美国的数据,可以看到美国信贷占GDP的比重在2008年达到最大,也是在这一年,次贷危机全面爆发.

从这里我们易于得出当信贷占GDP的比重达到高点时,会爆发金融危机的结论.比如美国2001年也到达一个高点,那一年附近美国互联网泡沫破灭.
但是日本前一个高点在1998,1999年附近,那两年似乎日本没有什么大的的危机发生?

2. 中国在2008年后开始高速加杠杆
中间绿色和棕色分别是中国和德国的数据,中贷款占GDP的比重与德国的水平相似,并且这两个国家的共同特点是当美日这一指标在2007年达到高点时,中德两国达到低点.
中国尤其特殊的地方是,当2008年后美德日三国都开始去杠杆的时候(表现为这一指标的下降),中国开始高速加杠杆,指标值快速上升.

3. 目前世界的信贷占GDP的比重处在历史上的最高水平.

世界1984-2005之间,世界总体的信贷占GDP的比重是比较平稳的,此后一直上升.

一个疑问:中国信贷占GDP的比重在2003年达到过一个高点,不知道那一年发生了什么?
