---
title: "市场观测指标"
author: "qiufei"
date: "2016-03-4"
output: 
  html_document: 
    fig_height: 7
    fig_width: 9
    keep_md: yes
    number_sections: yes
    theme: readable
    toc: yes
---

```{r setup,Message=FALSE,echo=FALSE,include=FALSE,warning=FALSE}

# load needed packages
library(knitr)
opts_chunk$set(Message=FALSE,echo=FALSE)
library(ggplot2)
library(reshape2)
library(Quandl)
library(quantmod)
options("getSymbols.warning4.0"=FALSE)
library(scales)
library(plyr)
library(dplyr)
options(warn=-1)                        #suprress warning globally
## the default is
## options(warn=0)
## 
##
## define needed functions
## 
simpic.f = function(code,label){
    raw = getSymbols.FRED(code,auto.assign=FALSE)
    raw.median = median(coredata(raw),na.rm = TRUE)
    detail = summary(raw)[,2]
    print(detail)
    chartSeries(raw,name = label)
}
## 
simpic.q = function(code,label){
    raw = Quandl(code, api_key="9iGeZZoG6Vc46rfs1AgJ")
    raw = as.xts(raw[,-1],order.by = raw[,1])
    detail = summary(raw)[,2]
    print(detail)
    chartSeries(raw,name = label)
}


```

# risk and volatility #

## St. Louis Fed Financial Stress Index ##

```{r}

simpic.f('STLFSI','St. Louis Fed Financial Stress Index')  

```


## CBOE volatility index ##

in the short run, there is a strong negative correlation between volatility index and the level of the market.

```{r volatility}

simpic.f('VIXCLS','CBOE Volatility Index')

simpic.f('VXOCLS','CBOE S&P 100 Volatility Index')

```


## BofA Merrill Lynch US Corporate AAA Option-Adjusted Spread ##

```{r}

simpic.f('BAMLC0A1CAAA','AAA Option-Adjusted Spread')  

```

## BofA Merrill Lynch US High Yield CCC or Below Option-Adjusted Spread ##

```{r}

simpic.f('BAMLH0A3HYC','CCC or Below Option-Adjusted Spread')  

```




# interest rates #

Long-Term Government Bond Yields

## USA Treasury Inflation-Indexed Security ##

```{r tips}

simpic.f('FII10','10-Year Treasury Inflation-Indexed Security, Constant Maturity')

simpic.f('TP30A28','30-Year Treasury Inflation-Indexed Bond')  

```

## 'Moody Seasoned Aaa Corporate Bond Yield ##
```{r}

simpic.f('AAA','Moody Seasoned Aaa Corporate Bond Yield')  

```

## Moody's Seasoned Aaa Corporate Bond Yield Relative to Yield on 10-Year Treasury Constant Maturity ##

```{r}

simpic.f('AAA10YM','Moody Seasoned Aaa  Relative to 10-Year Treasury Constant Maturity')  

```


## Effective Federal Funds Rate ##

```{r}

simpic.f('FEDFUNDS','Effective Federal Funds Rate')  

```




# stock markets #

1. historically stocks have returned between 6 and 7 percent after inflation over the last two centuries and have sold at an average PE ratio of about 15.




## s&p ##

of the top 20 firms,15 belongs to two industries: consumer staples and healthcare.

```{r sp500}

simpic.f('SP500','S&P 500')  

```


## Dow Jones Industrial Average ##

```{r dj}

simpic.f('DJIA','Dow Jones Industrial Average')



```

simpic.q('BCB/UDJIAD1','Dow Jones Industrial Average since 1896')


# real estate #

## USA home price ##


 
```{r shiller}

simpic.f('CSUSHPINSA','shiller home price index')

```
 Index Jan 2000=100

